Meta-analysis

### 2020-06-23 04_MetaAnalysis.Rmd
Edits corrections and testing the random effect struction of the meta-analysis

The use of these imputed MSE was giving a varied outcome each time it was run. 
The next code chunk removes the studies without variation to observe what the meta-analysis outcome would be.

@@

Let's simplify our data
```{r metafor_organisation}
dat1 <-
   slimmer_PM_dat %>%
   filter(fungicide_ai != "control") %>% #remove controls from the data
   mutate(spray_management =
             factor(
      spray_management,
      c( "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )))%>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype ,
      spray_management,
      fungicide_ai,
      D_pres,
      grain_yield.t.ha,
      grain_SMD,
      vi,
      vi2
   )
```

@@

Let's undertake the meta-analysis using the package `metafor`.
Ee are using the `spray_management` variable as a moderator and a interactive term to the `trial` random variable.
Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management -1,
   method = "ML",
   random = ~ spray_management|trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```
In this result we can see that the `Early` treatment is not significantly different to zero, which in this case is the mean of the no spray control. 
However the other treatments are significantly different to zero.
The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 85.232, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010]. 
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.48, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

AIC(PM_mv_St)
anova(PM_mv, PM_mv_St)
```
The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. So we will keep the original model `PM_mv`.

@@

```{r}
profile(PM_mv , tau2 = 1)
profile(PM_mv , tau2 = 2)
profile(PM_mv , tau2 = 3)
profile(PM_mv , tau2 = 4)
profile(PM_mv , tau2 = 5)
```

>>>>

The use of these imputed MSE was giving a varied outcome each time it was run. 
The next code chunk removes the studies without variation, given we can't reliably impute them.

@@

Let's simplify our data
```{r metafor_organisation}
dat1 <-
   slimmer_PM_dat %>%
   filter(fungicide_ai != "control") %>% #remove controls from the data
   mutate(spray_management =
             factor(
      spray_management,
      c( "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus")),
      TrialDose = factor(paste(trial, dose, sep = "_"))
      )%>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype ,
      spray_management,
      fungicide_ai,
      D_pres,
      grain_yield.t.ha,
      grain_SMD,
      vi,
      vi2
      )
```

@@

Let's undertake the meta-analysis using the package `metafor`.
We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.
```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management -1,
   method = "ML",
   random = ~ spray_management|trial,
   struct = "UN",
   data = dat1
)
summary(PM_mv)
```
In this result we can see that the `Early` treatment is not significantly different to zero, which in this case is the mean of the no spray control. 
However the other treatments are significantly different to zero.
The Qm [omnibus test](http://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept?s[]=anova) of moderators, show the moderators significantly influence the model ($Q_M = 85.232, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010]. 
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 47501.48, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

@@

dat1$trial[1]

PM_mv_St1 <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management,
   method = "ML",
   random = list(~ 1|location/year/trial_ref/dose/host_genotype/factor(row_spacing)/spray_management),
   data = dat1
)

AIC(PM_mv) # Printing the AIC of the model helps differentiate the models in the anova output
anova(PM_mv, PM_mv_St1) # PM_mv is the better model

The simpler `PM_mv_St` model explains significantly less variation as the more complicated model `PM_mv`. 
So we will keep the original model `PM_mv`.

@@

```{r rmaProfilePlots}
profile(PM_mv , tau2 = 1)
profile(PM_mv , tau2 = 2)
profile(PM_mv , tau2 = 3)
profile(PM_mv , tau2 = 4)
profile(PM_mv , tau2 = 5)
```
